Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-05-04 paper/main.tex
add table for COPE1 group results (AO & AV)

\paragraph{video contrasts of parameter estimate}
% ggf. irgendwo noch reinpressen, dass man damit fast alle schnitte in FG benutzt hat
We created a contrast presumably correlating with increased hemodynamic activity in the PPA by contrasting different kind of cuts.
This was done without controlling for the specific visual content depicted in the frame after each cut.
The cinematographic rationale was that - over the course of a movie - cuts shift from establishing the setting and the spatial relationships within a setting at the beginning of a movie to depicting persons and objects more relevant to the subsequently evolved narrative later in the movie {brown2012cinematography; mercado2011filmmakers}.
The neurocientific rationale was that activity in the PPA is greater when participants view novel versus repeated scenes resp. view-points \citep{epstein1999parahippocampal}.
Hence, we contrasted cuts to a setting occurring for the first time (vse\_new) and cuts within a locale depicted for the first time (vpe\_new) with shots to a recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).

@@

% generate-masks.py; DO NOT TOUCH!
% FOR GROUP:
% 0. In FSLeyes, manually created probabilistic brain lobe maps from \href{"https://doi.org/10.5281/zenodo.1470761"}{the MNI Structural Atlas} (./data/atlases/mni_prob_*.nii.gz)
% 1. these brain lobe maps were aligned (via FSL's flirt -applyxf with 12 dof) to the \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific T2* group template} (./data/atlases/grpbold3Tp2_mni_prob_*.nii.gz)
% 2. from \href{"https://github.com/psychoinformatics-de/studyforrest-data-visualrois"} {sengupta2016extension}: UNIlateral probabilistic group ROI masks (data/masks/*_overlap.nii.gz) -> BIlateral probabilistic & binary grp ROI masks in grp space (.data/masks/bilat_???_prob.nii & .data/masks/bilat_???_binary.nii )
% FOR SUBJECTS:
% 1. bilateral grp ROI masks in grp space -> bilateral grp ROI masks in subject space (applywarp; sub-??/masks/grp_*_bin.nii.gz)
% 2. probabilistic MNI mask -> subject space (via FSL's applywarp)
% 3. merge probabilistic occipital & temporal mask in subject space
%	(sub-??/masks/mni_prob_occip_tempo.nii.gz)
% 4. created subject-specific FOV from 4d 7t audio drama time series
%	(./sub-??/masks/ao_fov_mask.nii.gz)
% 5. individual, unilateral ROIs from {sengupta2016extension} were joined and co-registered to MNI 152 (1mm) space, and binarized
% 6. individual (un)thresholded zmaps (from the COPEs) were co-regi<wstered with MNI 152 (1mm) template.
\section{Results (audio)}
% vgl. mit Ergebnis-Teilen anderer Localizer (in wievielen VPN funktioniert's etc.)
% https://en.wikipedia.org/wiki/Bland%E2%80%93Altman_plot

\section{Results (movie)}
lore ipsum

>>>>

\paragraph{video contrasts of parameter estimate}
We created a contrast presumably correlating with increased hemodynamic activity in the PPA by contrasting different kind of cuts.
This was done without controlling for the specific visual content depicted in the frame after each cut.
The cinematographic rationale was that - over the course of a movie - cuts shift from establishing the setting and the spatial relationships within a setting at the beginning of a movie to depicting persons and objects more relevant to the subsequently evolved narrative later in the movie {brown2012cinematography; mercado2011filmmakers}.
The neurocientific rationale was that activity in the PPA is greater when participants view novel versus repeated scenes resp. view-points \citep{epstein1999parahippocampal}.
% ggf. irgendwo noch reinpressen, dass man damit fast alle schnitte in FG benutzt hat
Hence, we contrasted cuts to a setting occurring for the first time (vse\_new) and cuts within a locale depicted for the first time (vpe\_new) with shots to a recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).

@@

% generate-masks.py; DO NOT TOUCH!
% FOR GROUP:
% 0. In FSLeyes, manually created probabilistic brain lobe maps from \href{"https://doi.org/10.5281/zenodo.1470761"}{the MNI Structural Atlas} (./data/atlases/mni_prob_*.nii.gz)
% 1. these brain lobe maps were aligned (via FSL's flirt -applyxf with 12 dof) to the \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific T2* group template} (./data/atlases/grpbold3Tp2_mni_prob_*.nii.gz)
% 2. from \href{"https://github.com/psychoinformatics-de/studyforrest-data-visualrois"} {sengupta2016extension}: UNIlateral probabilistic group ROI masks (data/masks/*_overlap.nii.gz) -> BIlateral probabilistic & binary grp ROI masks in grp space (.data/masks/bilat_???_prob.nii & .data/masks/bilat_???_binary.nii )
% FOR SUBJECTS:
% 1. bilateral grp ROI masks in grp space -> bilateral grp ROI masks in subject space (applywarp; sub-??/masks/grp_*_bin.nii.gz)
% 2. probabilistic MNI mask -> subject space (via FSL's applywarp)
% 3. merge probabilistic occipital & temporal mask in subject space
%	(sub-??/masks/mni_prob_occip_tempo.nii.gz)
% 4. created subject-specific FOV from 4d 7t audio drama time series
%	(./sub-??/masks/ao_fov_mask.nii.gz)
% 5. individual, unilateral ROIs from {sengupta2016extension} were joined and co-registered to MNI 152 (1mm) space, and binarized
% 6. individual (un)thresholded zmaps (from the COPEs) were co-regi<wstered with MNI 152 (1mm) template.
\section{Results (audio)}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast \texttt{geo, groom > all non-geo} (audio-only stimulus).
Clusters sorted by voxel size.
The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
\label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & XYZ \\
164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & XYZ \\
83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & XYZ \\
73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & XYZ \\
63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & XYZ \\
37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & XYZ \\
\bottomrule
\end{tabular}
\end{table*}

\section{Results (movie)}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast \texttt{vse\_new > vpe\_old} (audio-visual stimulus).
Clusters sorted by voxel size.
The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
\label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 \\
\bottomrule
\end{tabular}
\end{table*}
